---
title: "Robustness Check"
subtitle: "of Centrality Measures"
author: "Raymond Andaya"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: lumen
    toc: true
    number_sections: true
    highlight: github
editor_options: 
  markdown: 
    wrap: 72
---

```{=html}
<style> body {text-align: justify} </style>
```
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(igraph)
library(visNetwork)
library(knitr)
library(Hmisc)
library(ggplot2)
library(reshape2)
library(corpcor)
library(corrplot)
```

# Reading The Data

I read the data 
with the help of `readxl` library.

The first 6 rows of data are shown below.

```{r}
#Read the file
f <- read.csv("1107poc-edges.csv")

kable(head(f),caption = "First 6 rows of dataset")
```

# Network Construction

I construct the network. The information about network is shown
below. There are 535 nodes and 6466 edges in the
network.

I computed network centrality measures. Centrality measures 
for the first 10 nodes are shown in the Table below.

```{r}
g <- graph.data.frame(f,directed = F)
g

#Compute Centrality Measures
df <- data.frame(Node = V(g)$name,
                 Betweenness = as.vector(betweenness(g)),
                 Eigen = as.vector(eigen_centrality(g)$vector))

kable(head(df,10),caption = "Centrality Scores for the first 10 nodes")
```

# Basic Concept of Robustness in Centrality

Let G be an undirected graph with vertix set `V(G)` and edge set `E(G)`.
A centrality measure `c` is a real-valued function that assigns
centrality values to all nodes in a graph and is invariant to
structure-preserving mappings. That is, centrality values depend solely
on the structure of a graph. External information (e.g., node or edge
attributes) has no influence on the centrality values (Koschützki et al
[1]). The centrality value for node `u ∈ V(G)` is denoted by `cG(u)` and
the centrality values for all nodes in `G(u1, u2, ... , un)`, by the
vector $$ c(G) := (c(u1), ... , c(un))$$ Let `G` and `G'` be two graphs
and `c` a centrality measure. A pair of nodes `u, v ∈ V(G) ∩ V(G')` and
`u != v` is called concordant w.r.t. `c` if both nodes have distinct
centrality values and the order of `u` and `v` is the same in `c(G)` and
`c(G')`. That is, either $$ cG(u) < cG(v) ;and; cG'(u) < cG'(v) $$

or $$ cG(u) > cG(v) ;and; cG'(u) > cG'(v) $$

A pair of nodes is called `discordant` if both nodes have distinct
centrality values and the order of `u` and `v` in `c(G)` differs from
the order of `u` and `v` in `c(G')`, that is, either
$$ cG(u) < cG(v) and cG'(u) > cG'(v) $$

or

$$ cG(u) > cG(v) and cG'(u) < cG'(v) $$ Ties are neither concordant nor
discordant.

Network data can be influenced by a variety of different measurement
errors. Wang et. al.[2] categorized measurement errors into different
groups i.e., `false-negative`, `false-positive` (nodes and edges). For
example, when 10% of the edges are missing in the measured network data,
the graph constructed from this observed data suffers from
`false-negative edges`.

# Robustness Check

Let `G` and `G'` denote graphs on the same vertex set and c a centrality
measure. To measure the robustness of `c` with respect to these two graphs, I
use Kendall's tau (`“tau-b”`) rank correlation coefficient (Kendall
[3]). Correlations are commonly used to measure the robustness of
centrality measures. Correlations are commonly used to measure the
robustness of centrality measures. Like existing studies, we also used
rank correlations to minimize the influence of outliers (Kim & Jeong
[4]; Lee & Pfeffer[5]; Wang et al [6]). I calculate the robustness ρ
for a centrality measure c with respect to `G` and `G'` as follows: \_
$$ pc(G,G') = \frac{n_c-n_d}{\sqrt{(n_c+n_d+n_t)*(n_c+n_d+n_t')}} $$
with `nc` as the number of concordant pairs and `nd` as the number of
discordant pairs w.r.t. the order given by `c(G)` and `c(G')`. Ties only
in `c(G)` are denoted by `nt`, ties only in `c(G')` by `nt'`. It follows
that the values of `ρc(G, G')` are in the interval
`[−1, 1]`.

In network studies, the measured network data often contains sampling
errors (Leecaster et al. [7]; Schulz [8]; Wang et al.[6]). The
robustness concept helps describe this impact: given the measured
network (after removing edges) `M`, the (unknown) hidden network
(without removing edges) `H`, and a centrality measure `c`, the
robustness `ρc(H, M)` measures the impact of the sampling error on the
centrality values of the nodes in the measured network.

The estimation approach is based on the observation that, given a graph
`G`, a centrality measure, and some error procedure, in many experiments
the robustness is nearly proportional to the error intensity. That is,
removing `20%` of the edges, randomly, has about twice as much impact on
the centrality measure as removing `10%` of the edges (Borgatti et al.
[9]; Frantz et al. [10]; Wang et al. [6]). Now let `G'` denote the graph
resulting from `G` by removing 10% of the edges, and let `G''` denote
the graph resulting from `G'` by removing 10% of the remaining edges.
One possible explanation for the observed linearity could be that the
robustness with respect to G and `G'` is close to the robustness with
respect to `G'` and `G''`, which is

$$ ρc(G, G') ∼ ρc(G', G'') $$ In our experiment,

-- first I removed `5%` edges and called it `g1`, -- then I removed
`5%` more edges from `g1` and called it `g2`, -- further I removed `5%`
more edges from `g2` and called it `g3`, -- lastly, I removed `5%`
edges from `g3` and called it `g4`.

I performed the 50 simulations of the above steps. In the end, I
computed the average betweenness and eigenvector centarlity score for the 50
simulations.

# Robustness Check of Betweenness

```{r}
# Function to compute betweenness centrality
GetBet <- function(g) {
lst <- list()
lst$g1 <- 0  
lst$g2 <- 0
lst$g3 <- 0
lst$g4 <- 0
for (i in 1:50) {
g1 <- delete_edges(g,sample(E(g),as.integer(ecount(g)*0.05))) #Del 5% edges
g2 <- delete_edges(g1,sample(E(g1),as.integer(ecount(g1)*0.05))) #Del 5% edges
g3 <- delete_edges(g2,sample(E(g2),as.integer(ecount(g2)*0.05))) #Del 5% edges
g4 <- delete_edges(g3,sample(E(g3),as.integer(ecount(g3)*0.05))) #Del 5% edges

lst$g1 <- lst$g1 + betweenness(g1)  
lst$g2 <- lst$g2 + betweenness(g2)
lst$g3 <- lst$g3 + betweenness(g3)
lst$g4 <- lst$g4 + betweenness(g4)
}
return(lst)
}

bet <- GetBet(g)
bet$g <- betweenness(g)
```

## Kendal's Tau Correlation Calculation

```{r}
v <- vector()
r=1
for (i in 1:5) {
  for (j in 1:5) {
    v[r] <- cor.test(as.vector(bet[[i]]),as.vector(bet[[j]]),method = "kendall")$estimate[[1]]
    r = r + 1
  }
}
bet_kmat <- matrix(v,nrow = 5,ncol = 5)
colnames(bet_kmat) <- c("G1","G2","G3","G4","G")
rownames(bet_kmat) <- c("G1","G2","G3","G4","G")
bet_kmat
corrplot(bet_kmat,method = "number",type = "lower")
```

## Gamma Correlation Calculation

```{r}
v <- vector()
r=1
for (i in 1:5) {
  for (j in 1:5) {
    v[r] <- rcorr.cens(as.vector(bet[[i]]),as.vector(bet[[j]]),outx = T)[[2]]
    r = r + 1
  }
}
bet_gmat <- matrix(v,nrow = 5,ncol = 5)
colnames(bet_gmat) <- c("G1","G2","G3","G4","G")
rownames(bet_gmat) <- c("G1","G2","G3","G4","G")
bet_gmat
corrplot(bet_gmat,method = "number",type = "lower")
```

The output gives explicit data about the calculation
being made, including pairs that were thrown out due to "ties", the
number of concordant pairs, and so on. The most important piece of output
here is correlation score, which is the gamma statistic. For this
example, the generated data has a strong positive relationship (almost
0.99). The Gamma correlation proves that the betweenness
centrality do not have robust results. These results shows that top ranked
nodes in the true network (G), are relatively the same top ranked nodes in
the observed networks (G1...G4).

I found the same in the case of Kendal's Correlation, where the data
has a strong positive relationship.

## Line chart for Gamma and Kendall Correlation

The below charts shows the correlation of centrality score between the
original network (G), and measured networks (G1...G4). This correlation
helps to check the robustness of centrality scores. The Figures below
shows the Kendall and Gamma correlation between centrality scores.

```{r}
df <- data.frame(Kendal = bet_kmat[,5],
                 Gamma = bet_gmat[,5],
                 Graph = rownames(bet_gmat))

#Combine the data
melted <- melt(df, id.vars=c("Graph"))

p <- ggplot(melted, aes(Graph, value, color = variable)) +
    geom_line(aes(group=paste0(variable))) + 
    geom_point() + 
    labs(title="Betweenness Centrality",
         subtitle = "Correlation b/w Hidden (G) and Measured Graphs (G1...G4)",
         x ="Graphs", y = "Correlation")
p
```

# Robustness Check of Eigen Centrality

The same procudre is used to check the robustness of eigenvector centrality.
Here, I find the correlation between the eigenvector centrality of the original
network and the measured networks.

```{r}
# Function to compute betweenness centrality
GetEigen <- function(g) {
lst <- list()
lst$g1 <- 0  
lst$g2 <- 0
lst$g3 <- 0
lst$g4 <- 0
for (i in 1:50) {
g1 <- delete_edges(g,sample(E(g),as.integer(ecount(g)*0.05))) #Del 5% edges
g2 <- delete_edges(g1,sample(E(g1),as.integer(ecount(g1)*0.05))) #Del 5% edges
g3 <- delete_edges(g2,sample(E(g2),as.integer(ecount(g2)*0.05))) #Del 5% edges
g4 <- delete_edges(g3,sample(E(g3),as.integer(ecount(g3)*0.05))) #Del 5% edges

lst$g1 <- lst$g1 + eigen_centrality(g1)$vector 
lst$g2 <- lst$g2 + eigen_centrality(g2)$vector
lst$g3 <- lst$g3 + eigen_centrality(g3)$vector
lst$g4 <- lst$g4 + eigen_centrality(g4)$vector
}
return(lst)
}

eig <- GetEigen(g)
eig$g <- eigen_centrality(g)$vector
```

## Kendal's Tau Correlation Calculation

```{r}
v <- vector()
r=1
for (i in 1:5) {
  for (j in 1:5) {
    v[r] <- cor.test(as.vector(eig[[i]]),as.vector(eig[[j]]),method = "kendall")$estimate[[1]]
    r = r + 1
  }
}
eig_kmat <- matrix(v,nrow = 5,ncol = 5)
colnames(eig_kmat) <- c("G1","G2","G3","G4","G")
rownames(eig_kmat) <- c("G1","G2","G3","G4","G")
eig_kmat
corrplot(eig_kmat,method = "number",type = "lower")
```

## Gamma Correlation Calculation

```{r}
v <- vector()
r=1
for (i in 1:5) {
  for (j in 1:5) {
    v[r] <- rcorr.cens(as.vector(eig[[i]]),as.vector(eig[[j]]),outx = T)[[2]]
    r = r + 1
  }
}
eig_gmat <- matrix(v,nrow = 5,ncol = 5)
colnames(eig_gmat) <- c("G1","G2","G3","G4","G")
rownames(eig_gmat) <- c("G1","G2","G3","G4","G")
eig_gmat
corrplot(eig_gmat,method = "number",type = "lower")
```

In the Correlation, I found the same results as did in for
betweenness centrality. The data shows a strong positive correlation.

## Line chart for Gamma and Kendall Correlation

```{r}
df <- data.frame(Kendal = eig_kmat[,5],
                 Gamma = eig_gmat[,5],
                 Graph = rownames(eig_gmat))

#Combine the data
melted <- melt(df, id.vars=c("Graph"))

p <- ggplot(melted, aes(Graph, value, color = variable)) +
    geom_line(aes(group=paste0(variable))) + 
    geom_point() + 
    labs(title="Eigen Centrality",
         subtitle = "Correlation b/w Hidden (G) and Measured Graphs (G1...G4)",
         x ="Graphs", y = "Correlation")
p
```


# References

[1] Koschützki, D., Lehmann, K., & Peeters, L. (2005). Centrality
Indices. In U. Brandes, & T. Erlebach (eds.), Network Analysis:
Methodological Foundations, 16--61. Springer Berlin Heidelberg.

[2] Wang, C., Butts, C. T., Hipp, J. R., Jose, R., & Lakon, C. M.
(2016). Multiple imputation for missing edge data: A predictive
evaluation method with application to Add Health. Social Networks, 45,
89--98.

[3] Kendall, M. G. (1945). The treatment of ties in ranking problems.
Biometrika, 33(3), 239--251.

[4] Kim, P. J., & Jeong, H. (2007). Reliability of rank order in sampled
networks. European Physical Journal b, 55(1), 109--114

[5] Lee, J.-S., & Pfeffer, J. (2015). Robustness of network centrality
metrics in the context of digital communication data. In Proceedings of
the 48th Hawaii international conference on system sciences.

[6] Wang, D. J., Shi, X., McFarland, D. A., & Leskovec, J. (2012).
Measurement error in network data: A re-classification. Social Networks,
34(4), 396--409.

[7] Leecaster, M., Toth, D. J. A., Pettey, W. B. P., Rainey, J. J., Gao,
H., Uzicanin, A., & Samore, M. (2016). Estimates of social contact in a
middle school based on self-report and wireless sensor data. Plos One,
11(4).

[8] Schulz, J. (2016). Using Monte Carlo simulations to assess the
impact of author name disambiguation quality on different bibliometric
analyses. Scientometrics, 107(3), 1283--1298.

[9] Borgatti, S. P., Carley, K. M., & Krackhardt, D. (2006). On the
robustness of centrality measures under conditions of imperfect data.
Social Networks, 28(2), 124--136.

[10] Frantz, T. L., Cataldo, M., & Carley, K. M. (2009). Robustness of
centrality measures under uncertainty: Examining the role of network
topology. Computational and Mathematical Organization Theory, 15(4),
303--328.
